\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2015-03-05 Report/project_report.tex
Added citation for loosely coupled

Visual-inertial navigation systems (VINS) have been applied broadly in robotics \cite{Mourikis:2007:ICRA, Sibley:2010:JFR, Huster:2002:OC, Kottas:2013:IROS, Kim:2007:RSS, Li:2013coa,  You:2001:VR}, and there is a considerable body of work covering a wide range of estimation algorithms for the camera-IMU sensor pair. 
These techniques are often characterized as either \textit{loosely coupled} or \textit{tightly coupled}.
In loosely coupled systems, image and IMU measurements are processed individually before being fused into a single estimate, while tightly coupled systems process all information together.  
The decoupling of inertial and visual measurements in loosely coupled systems leads to inexpensive computations, but at the cost of information: processing camera and IMU measurements separately makes optimal estimation of biases impossible \cite{Li:2013coa}. 
In this work, we consider tightly coupled algorithms, which are preferable for accurate and consistent visual-inertial navigation.

>>>>

Visual-inertial navigation systems (VINS) have been applied broadly in robotics \cite{Mourikis:2007:ICRA, Sibley:2010:JFR, Huster:2002:OC, Kottas:2013:IROS, Kim:2007:RSS, Li:2013coa,  You:2001:VR}, and there is a considerable body of work covering a wide range of estimation algorithms for the camera-IMU sensor pair. 
These techniques are often characterized as either \textit{loosely coupled} or \textit{tightly coupled}.
In loosely coupled systems, image and IMU measurements are processed individually before being fused into a single estimate, while tightly coupled systems process all information together.  
The decoupling of inertial and visual measurements in loosely coupled systems limits computational complexity \cite{Leutenegger:2015:IJRR}, but at the cost of information: processing camera and IMU measurements separately makes optimal estimation of biases impossible \cite{Li:2013coa}. 
In this work, we consider tightly coupled algorithms, which are preferable for accurate and consistent visual-inertial navigation.
